Supplementary material to:  On the propriety of restricted Boltzmann machines

### 2016-12-11 writing/appendix/appendix-center.Rmd
slides start

---
title: "Supplementary Material to:  On the propriety of restricted Boltzmann machines"
author: "Andee Kaplan, Daniel Nordman, and Stephen Vardeman"
date: "November, 2016"
linestretch: 2 
output: 
  pdf_document:
    fig_caption: yes
    includes:
      in_header: ../latex/header.tex
    number_sections: yes
---

>>>>

---
title: "Supplementary material to:  On the propriety of restricted Boltzmann machines"
author: 
  - name: Andee Kaplan
    university: Iowa State University
    department: Department of Statistics
  - name: Daniel Nordman
    university: Iowa State University
    department: Department of Statistics
  - name: Stephen Vardeman
    university: Iowa State University
    department: |
      | Department of Statistics and Industrial Manufacturing 
      | Systems Engineering Department
output: 
  pdf_document:
    fig_caption: yes
    includes:
      in_header: ../latex/header.tex
    number_sections: yes
    template: ../latex/technometrics_article.tex
fontsize: 12pt
blind: false
---
